---
title: "Weighted averaged ensembles with genetic algorithms"
author: "Miguel Conde"
date: "21 de noviembre de 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Let's suppose we have a training set with $N$ observations, each made of $M$ features values, and a target real variable, $y$.
We build $k$ regression models ($m_i$) to estimate $y_i$ as $\hat{y}_i$.

We are interested in building a weighted averaged ensemble this way:

$$
\hat{y}^{ens}_i = \sum_{j=1}^{k}{w_j\hat{y}_{ij}}
$$


Let $y_i$ be:
```{r}
N = 100

y <- sin(seq(0, 2*pi, length.out = 100))
```

Let's simulate now the $k$ estimates.
```{r}
mn1 <- 0
mn2 <- 0.5
mn3 <- -0.5
sd1 <- 0.1
sd2 <- 0.1
sd3 <- 0.1

set.seed(6789)
y_hat <- data.frame(y_hat_m1 = y + rnorm(N, mn1, sd1),
                    y_hat_m2 = y + rnorm(N, mn2, sd2),
                    y_hat_m3 = y + rnorm(N, mn3, sd3))
```

We need this code:
```{r, message=FALSE, warning=FALSE}
source("gaWARE.R")
```

Let's check the fitness function:

```{r}
# Check
fitness_gaWARE(w = c(1, 0, -1), y = y, y_hat = y_hat,
               maximize = TRUE, perfFunc = RMSE)

fitness_gaWARE(w = c(1, 0, -1), y = y, y_hat = y_hat,
               maximize = FALSE, perfFunc = myMAE)
```

Okay, let's look for our ensemble parameters:

```{r}
# Ranges of parameters to estimate
minVector <- c(-10, -10, -10) # w1, w2, w3
maxVector <- c(10, 10, 10)

# Optimization (In this example: COST FUNCTION = myMAE())
GA <- ga(type = "real-valued",
         fitness = function(x, ...) fitness_gaWARE(x, ...),
         ## '...' for fitness_gaWARE()
         y = y, y_hat = y_hat,
         maximize = FALSE, perfFunc = myMAE,
         ##
         min = minVector, max = maxVector, popSize = 50,
         maxiter = 100, names = c("w1", "w2", "w3"),
         seed = 789,
         monitor = NULL)

summary(GA)
GA@solution
```

```{r include=FALSE}
w <- drop(GA@solution)
```
And our ensemble is:

$$
\hat{y}^{ens}_i = \sum_{j=1}^{k}{w_j\hat{y}_{ij}} = `r w[1]`\times\hat{y}_i + `r w[2]`\times\hat{y}_i + `r w[2]`\times\hat{y}_i 
$$

```{r}
y_hat_ens <- as.matrix(y_hat) %*% t(GA@solution)
```





