---
title: "Weighted average ensambles with 1-layer neural networks"
author: "Miguel Conde"
date: "22 de noviembre de 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.align = "center")
```

We will work again with this setup:

Let's suppose we have a training set with $N$ observations and a target real variable, $y_i$, $i=1...N$.
Upon the $N$ observations we can build $k$ regression models ($M_m$, $m=1,...k$) to estimate each $y_i$ as $\hat{y}_i^m$.


We are interested in building a weighted average ensemble this way:

$$
\hat{y}^{ens}_i = \sum_{m=1}^{k}{w_m\hat{y}_i^m}
$$

where:

*  $\hat{y}^{ens}_i$ is the ensemble estimate of $y_i$
*  $\hat{y}_i^m$ is the model $m$ estimate of $y_i$
*  $w_m$ is the weight assigned in the ensemble to the model $m_i$

Let $y_i$ be:

```{r}
N = 100

y <- sin(seq(0, 2*pi, length.out = 100))
```

Let's simulate now the estimates of $k=3$ models.
```{r}
mn1 <- 0
mn2 <- 0.5
mn3 <- -0.5
sd1 <- 0.1
sd2 <- 0.1
sd3 <- 0.1

set.seed(6789)
y_hat <- data.frame(y_hat_m1 = y + rnorm(N, mn1, sd1),
                    y_hat_m2 = y + rnorm(N, mn2, sd2),
                    y_hat_m3 = y + rnorm(N, mn3, sd3))
```

This time we are going to use a 1-hide layer neural network to obtain an optimized set of weights $w_m$.

We'll take advantage of `caret` package functionalities:

```{r}
require(caret)
modelLookup("neuralnet")
```

We need a function for our optimization function, `mae()` in this case:

```{r}
require(Metrics)

myMAESummary <- function(data, lev = NULL, model = NULL) {
  out <- c(postResample(data[, "pred"], data[, "obs"]),
           mae(actual = data[,"obs"], predicted = data[,"pred"]))
  names(out)[3] <- "MAE"
  out
}
```


```{r}
trCtrl <- trainControl(method = "cv", 
                       number = 10, 
                       summaryFunction = myMAESummary)
# nnet
# tnGrd <- expand.grid(size = 1,
#                      decay = c(0, 10^seq(-1, -4, length = 5 - 1)))

# neuralnet
tnGrd <- expand.grid(layer1 = 1, layer2 = 0, layer3 = 0)

# dnn
# tnGrd <- expand.grid(layer1 = 1, layer2 = 0, layer3 = 0,
#                      hidden_dropout = 0, visible_dropout = 0)

set.seed(5678)

nnetM  <- train(x = y_hat,
                y = y,
                method = "neuralnet", # "neuralnet", "nnet", "dnn"
                act.fct = function(x) {x},
                metric = "MAE", 
                maximize = FALSE,
                trControl = trCtrl,
                # tuneLength = 5
                tuneGrid = tnGrd
                )

```

```{r}
nnetM
```

```{r}
summary(nnetM)
```

Thanks to [Visualizing neural networks in R – update](https://beckmw.wordpress.com/2013/11/14/visualizing-neural-networks-in-r-update/) we can visualize the network:
```{r}
# library(devtools)
# source_url('https://gist.githubusercontent.com/fawda123/7471137/raw/466c1474d0a505ff044412703516c34f1a4684a5/nnet_plot_update.r')
 
# plot.nnet(nnetM$finalModel)

plot(nnetM$finalModel)

```

The weights are:
```{r}
l1_wts <- nnetM$finalModel$weights[[1]][[1]]
l2_wts <- nnetM$finalModel$weights[[1]][[2]]
l1_wts
l2_wts
```

And our ensemble can be calculated as:


$$
(`r l1_wts[2,1]` \times \hat{y}^m_1 + `r l1_wts[3,1]` \times \hat{y}^m_2 + `r l1_wts[4,1]` \times \hat{y}^m_3 - `r l1_wts[1,1]`) \times `r l2_wts[2,1]` + `r l2_wts[1,1]` = \\ 
`r l1_wts[2,1] * l2_wts[2,1]` \times \hat{y}^m_1 + `r l1_wts[3,1] * l2_wts[2,1]` \times \hat{y}^m_2 + `r l1_wts[4,1] * l2_wts[2,1]` \times \hat{y}^m_3 + (`r l1_wts[1,1] * l2_wts[2,1] + l2_wts[1,1]`  )
$$


In R:
```{r}
y_hat_ens <- cbind(1, (as.matrix(cbind(1,y_hat)) %*% l1_wts)) %*% l2_wts
```

```{r}
head(y_hat_ens)
```
```{r}
head(predict(nnetM, y_hat))
```


# Session Info
```{r}
sessionInfo()
```